\sectionTitle{Projects}{\faLaptop}

\begin{projects}
        \project
	{SMG Station — Personal Hub} {Mar 2026 - Present}
	{{\textbf{Architect \& Developer} (Digital Sandbox)}}
	{Engineered a high-performance, real-time Elixir umbrella application powered by Phoenix LiveView and Erlang/OTP. Features 10+ concurrent modules (multiplayer chess engine, real-time Kanban calendars, document viewers, typing games) running completely in-memory with zero client-side frameworks or heavy databases, leveraging WebSockets and stateful GenServers for real-time synchronization.}
	{Elixir, Erlang/OTP, Phoenix LiveView, WebSockets, Tailwind CSS, Docker, Caddy}

        \project
	{Tech Meemer SMG — Autonomous AI Agent} {Dec 2025 - Feb 2026}
	{{\textbf{Architect \& Developer} (Automated Pipeline)}}
	{Designed and deployed an autonomous content generation agent using Node.js and SQLite. Programmed scheduled cron loops to scrape trending technology feeds, orchestrate multi-agent prompts utilizing Google Gemini 2.0 Flash and Groq LLMs for joke synthesis, and automatically render and publish graphic nodes via the Instagram Graph API and Imgflip API.}
	{Node.js, SQLite, Google Gemini, Groq, Instagram API, Docker, Cron scheduling}

        \project
	{SMG Idea Engine — Visionary AI Brainstorm Node} {May 2026 - Present}
	{{\textbf{Architect \& Developer} (AI Integration)}}
	{Engineered a rapid-response AI brainstorming engine exposing RESTful endpoints for architectural idea generation and logical simulation. Utilized the Groq SDK with LLaMA 3 70B for ultra-fast, structured JSON synthesis based on randomized technical seeds and custom analytical frameworks.}
	{Node.js, Express, Groq SDK, LLaMA 3, Docker, REST API}

        \project
	{Smart Parking System with Image Processing}{Aug 2017 - Aug 2018}
	{{\textbf{Final Semester Project} (IoT Integration)}}
	{Developed an innovative Smart Parking System utilizing ultrasonic sensors and custom MATLAB image processing algorithms to automate parking space allocation and real-time billing. Successfully integrated hardware layers (Arduino) with a relational database (MySQL) to reduce average parking search times by over 40\%.}
	{Arduino, MATLAB, MySQL, Image Processing, IoT Sensors}

        \project
	{Autonomous Self-Balancing Robotics Platform}{June 2017 - Dec 2017}
	{{\textbf{Research Intern} (Hardware Control \& DSP)}}
	{Engineered a two-wheeled self-balancing robot utilizing the Arduino Mega 2560 and MPU-6050 gyroscope/accelerometer sensors. Developed intricate PID control algorithms and real-time stability adjustment loops in Assembly/C to maintain center-of-gravity balance under variable payloads.}
	{Arduino Mega, MPU-6050 IMU, PID Control, Assembly C, Motor Drivers}
\end{projects}